---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

<style>
body {
  padding-top:0px
}
.navbar{
  visibility: hidden
}
.col3 {
  columns: 3 150px;         /* number of columns and width in pixels*/
  -webkit-columns: 3 150px; /* chrome, safari */
  -moz-columns: 3 1500px;    /* firefox */
}
</style>

<font size="6"><b>That's a wrap!</b></font>

<font size="4">

Put a bow on the 2018 Southeast Region Refuge and Hatchery iNaturalist Bioblitz!

Thanks to the hundreds of participating naturalists at more than 100 regional refuges and hatcheries!

Please consider these results <b>unofficial</b> until a formal announcement of the winners is made.

Enjoy some unofficial numbers while you wait on the official results/announcements:
<ul>
  <li>&gt; 16,000 observations</li>
  <li>&gt; 10,500 observations identified by the community to species</li>
  <li>&gt; 700 contributors</li>
</ul>

Compared to the same time period last year:
<ul>
  <li>&gt; 69% increase in observations</li>
  <li>&gt; 52% increase in observations identified to species</li>
  <li>&gt; 51% increase in unique species observed</li>
  <li>&gt; 8% <b>decrease</b> in unique contributors (interesting!)</li>
  <li>&gt; 9% increase in contributors making &ge;5 observations</li>
  <li>7% increase in number of participating refuges</li>
</ul>

</font>

### Bio-blitz links of interest

- [Bio-blitz contest announcement](https://drive.google.com/open?id=177ORN3RcpGUk6twn0FypOmz_LeWVI1FS){target="_blank"}
- [Bio-blitz FAQ](https://drive.google.com/open?id=10Ssf4UJP61JTi5VENJacopY7kobVI4Ea){target="_blank"}
- iNaturalist tips of the week: 
<div class="col3">
    - Tip 1: [Turning off auto upload](https://drive.google.com/open?id=1egVqzTDPUHmiaIquHTDfOF8Xrh0t7z5c){target="_blank"}
    - Tip 2: [Taking photos outside of the iNaturalist app](https://drive.google.com/open?id=1EEYeXkgR7gf0f1KzCTJ95YN6hx-lFF5x){target="_blank"}
    - Tip 3: [Tracking observations on your favorite refuges and hatcheries](https://drive.google.com/open?id=1xEJdFh408I3hpAm26cjC7WmZMpOsK7-b){target="_blank"}
    - Tip 4: [Finding observations in need of further verification](https://drive.google.com/open?id=1V48dCDFyOGUogpCTBzcPjGtRO8Y6IZNQ){target="_blank"}
    - Tip 5: [Improving photos for species ID](https://drive.google.com/open?id=10IUbuKBYMcPJrlIQ5UlNKy2Koav8J9zd){target="_blank"}
    - Tip 6: [iNaturalist value and harness subject matter experts](https://drive.google.com/open?id=1T-VSXcJAsjQoGfxhz6Xv6MhOd3G3e7L3){target="_blank"}
</div>

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(flexdashboard, DT, fwsinat, dplyr, tidyr)
source("./R/harvest_and_update.R")

# update_contest_recs(harvest = FALSE)

nwr18 <- readRDS("./output/nwr18_stats.rds")
nfh18 <- readRDS("./output/nfh18_stats.rds")

# Contest boundaries
start_date <- "2018-06-01"
end_date <- "2018-11-30"

all_recs <- bind_rows(nwr18, nfh18) %>%
  mutate(orgname = itistools::Cap(orgname),
         orgname = gsub("National Wildlife Refuge", "NWR", orgname),
         orgname = gsub("National Fish Hatchery", "NFH", orgname),
         orgname = gsub(" And Conservation Area", "/CA", orgname),
         orgname = gsub("D'arbonne", "D'Arbonne", orgname)) %>%
  filter(date <= as.Date(end_date))
spp_recs <- all_recs %>%
  filter(itis_taxon_rank %in% c("Genus", "Species", "Subspecies", "Variety"),
         grade == "research")

contest_recs <- all_recs %>%
  filter(date >= as.Date(start_date))

contest_recs_spp <- contest_recs %>%
  filter(itis_taxon_rank %in% c("Genus", "Species", "Subspecies", "Variety"),
         grade == "research")

ndays <- 0L
```

Dashboard
=======================================================================

Row
-----------------------------------------------------------------------

### Leaderboards last updated

```{r}
valueBox(value = format(Sys.time(), '%d %B, %Y'), icon = "glyphicon-calendar")
```

### Unique taxa documented

```{r}
valueBox(n_distinct(contest_recs_spp$sci_name), icon = "glyphicon-camera")
```

### Unique contributors

```{r}
valueBox(value = n_distinct(contest_recs$user), icon = "glyphicon-user")
```

### Refuges/Hatcheries with entries

```{r}
valueBox(n_distinct(contest_recs$orgname), icon = "glyphicon-leaf")
```

### BioBlitz days remaining

```{r}
valueBox(value = ndays, icon = "glyphicon-time")
```

Row
-----------------------------------------------------------------------

### **MOST SPECIES** {data-width=333}

```{r}
most_spp <- spp_recs %>%
  filter(date >= as.Date(start_date)) %>%
  group_by(orgname) %>%
  summarize(n_spp = n_distinct(sci_name)) %>%
  mutate(rank = rank(-1 * n_spp, ties = "min")) %>%
  select(rank, orgname, n_spp) %>%
  arrange(rank, orgname)
names(most_spp) <- c("Rank", "Refuge or Hatchery", "# Total Species")

DT::datatable(most_spp, rownames = FALSE, options = list(
  pageLength = 15,
  columnDefs = list(list(width = '20px', targets = 0),
                    list(width = '60px', targets = 2),
                    list(className = 'dt-left', targets = 1))))
```

### **MOST NEW SPECIES** {data-width=333}

```{r}
# Most new species
spp_before <- spp_recs %>%
  filter(date < as.Date(start_date)) %>%
  group_by(orgname) %>%
  summarize(before_spp = n_distinct(sci_name))

spp_after <-  spp_recs %>%
  group_by(orgname) %>%
  summarize(after_spp = n_distinct(sci_name))

most_new <- left_join(spp_after, spp_before, by = "orgname") %>%
  mutate(before_spp = ifelse(is.na(before_spp), 0, before_spp),
         n_new_spp = after_spp - before_spp,
         rank = rank(-1 * n_new_spp, ties = "min")) %>%
  select(rank, orgname, n_new_spp) %>%
  filter(n_new_spp > 0) %>%
  arrange(rank, orgname)
names(most_new) <- c("Rank", "Refuge or Hatchery", "# New Species")

DT::datatable(most_new,  rownames = FALSE, options = list(
  pageLength = 15,
  columnDefs = list(list(width = '20px', targets = 0),
                    list(width = '60px', targets = 2),
                    list(className = 'dt-left', targets = 1))))
```

### **MOST UNIQUE CONTRIBUTORS (≥ 5 records)** {data-width=333}

```{r}
most_users <- contest_recs %>%
  group_by(orgname, user) %>%
  summarize(n_recs = n()) %>%
  filter(n_recs >= 5) %>%
  group_by(orgname) %>%
  summarize(n_users = n_distinct(user)) %>%
  mutate(rank = rank(-1 * n_users, ties = "min")) %>%
  select(rank, orgname, n_users) %>%
  arrange(rank, orgname)
names(most_users) <- c("Rank", "Refuge or Hatchery", "# Total Users")

DT::datatable(most_users,  rownames = FALSE, options = list(
  pageLength = 15,
  columnDefs = list(list(width = '20px', targets = 0),
                    list(width = '60px', targets = 2),
                    list(className = 'dt-left', targets = 1))
))
```

```{r upload, eval = FALSE}
markdown::rpubsUpload("Region 4 Refuge and Hatchery iNaturalist Bioblitz 2018 - Contest Leaderboards",
                      "unofficial_final_leaderboard.html",
                      "https://api.rpubs.com/api/v1/document/391845/d5466570ba89463c90e2a6edde57691c",
                       method = "internal")
```